Population structure and phenotypic variation of *Sclerotinia sclerotiorum* from dry bean in the United States

### 2017-07-11 doc/manuscript/manuscript.Rmd

The dbRDA was performed on clone-corrected isolates (N = 318) after grouping them by location, host, region, and year.
The forward-backward selection process revealed aggressiveness, year, region, and host to be the optimal variables for the reduced model, accounting for 17.6% of the variation.
ANOVA revealed that the reduced model was significant with an adjusted R^2^ of 0.032 (P = 0.001).
The marginal effects of state, host, and year were also significant (P = 0.001), but aggressiveness was not significant (P = 0.045).
Much of the variation appears to be driven by isolates from Mexico (Fig. \@ref(rda-biplot)) and 2005, but it's worth noting that all Mexican isolates were collected in 2005.
Variance partitioning of the independent variables indicated aggressiveness to be the least influential factor with 0.1% contributing to explaining the variation of molecular data whereas the combination of variables accounted for 3.3%.

>>>>

The dbRDA was performed on clone-corrected isolates (N = 318) after grouping them by location, host, region, and year.
The forward-backward selection process revealed severity, year, region, and host to be the optimal variables for the reduced model, accounting for 17.6% of the total variation.
ANOVA revealed that the reduced model was significant with an adjusted R^2^ of 0.033 (P = 0.001).
Assessment of the marginal effects showed that state, host, and year significantly explained genetic variation (P = 0.001), but aggressiveness was only mildly significant (P = 0.045). 
Much of the variation appears to be driven by isolates from Mexico (Fig. \@ref(rda-biplot)) and 2005; it's worth noting that all Mexican isolates were collected in 2005.
Variance partitioning of the independent variables indicated aggressiveness to be the least influential factor with 0.1% contributing to explaining the variation of molecular data whereas the combination of variables accounted for 3.3%.
